method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update Ms.

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
data_ER$block[data_ER$trigger == 23] <- "3_distraction"
data_ER$block[data_ER$trigger == 24] <- "4_distancing"
data_ER$block[data_ER$trigger == 25] <- "5_suppression"
data_ER$block[data_ER$trigger == 26] <- "6_choice"

@@

Ratings_view <- data_ER %>%
  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

@@

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

@@

# Bayes Factors
EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf)

EMGLevReg_con <- cbind(EMGLevReg_con,
                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
                                                    df_error = EMGLevReg_con$df,
                                                    ci = 0.95),digits = 2))

colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
EMGLevReg_con[6,1] <- "$Distancing - Suppression$"

@@

# figure
FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
<!-- Attention! OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

## 2.1 Ethics information

>>>>

for (i in 1:nrow(data_ER)) {

  if (data_ER$trigger[i] == 21) {

    data_ER$block[i] = "view_neu"

  } else if (data_ER$trigger[i] == 22) {

    data_ER$block[i] = "view_neg"

  } else if (data_ER$trigger[i] == 23 ) {

    data_ER$block[i] = "distraction"

  } else if (data_ER$trigger[i] == 24 ) {

    data_ER$block[i] = "distancing"

  } else if (data_ER$trigge[i] == 25 ) {

    data_ER$block[i] = "suppression"

  } else if (data_ER$trigger[i] == 26) {

    data_ER$block[i] = "choice"
  }
}

@@

Ratings_view <- data_ER %>%
  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

@@

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

@@

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ... <!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al. --> for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED 
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private --> 
## 2.1 Ethics information

<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.
